---
title: "case study"
author: "Luan Mengxiao"
date: 2023-10-10
output: html_document
---

# set up

```{r, message = FALSE}
library(tidyverse)
library(ggridges)
library(leaflet)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


# import data

```{r}
library(p8105.datasets)
data(nyc_airbnb)

nyc_airbnb = 
  nyc_airbnb |>
  rename(borough = neighbourhood_group) |>
  mutate(stars = review_scores_location / 2)
```

# brainstorm questions

* Where are airbnbs expensive?
  - Borough? Neighbourhood?
  - Do other factors (room type) affect price? What about rating?
* How long are airbnbs active?
  - Are they illegal and do they get shut down?
* Which units have the most availability?
* How is review score impacted by location?
* How many apts are run by one host

# do some EDA

```{r}
nyc_airbnb |>
  count(borough)
```

```{r}
nyc_airbnb |>
  group_by(borough, room_type) |>
  summarize(mean_price = mean(price)) |>
  pivot_wider(
    names_from = room_type,
    values_from = mean_price
  )

nyc_airbnb |>
  group_by(borough, room_type) |>
  summarize(median_price = median(price)) |>
  pivot_wider(
    names_from = room_type,
    values_from = median_price
  )
```

```{r}
nyc_airbnb |>
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(borough~room_type)
```

```{r}
nyc_airbnb |>
  filter(price >= 9500)
```

```{r}
nyc_airbnb |>
  filter(price < 1000, room_type == "Entire home/apt") |>
  ggplot(aes(x = price)) +
  geom_histogram() +
  facet_grid(.~borough)
```

```{r}
nyc_airbnb |>
  filter(price < 1000, 
         room_type == "Entire home/apt", 
         borough == "Manhattan") |>
  group_by(neighbourhood) |>
  summarize(
    n_apt = n(),
    mean_price = mean(price)) |>
  arrange(desc(mean_price))
```

```{r}
nyc_airbnb |>
  filter(price < 1000, 
         room_type == "Entire home/apt", 
         borough == "Manhattan") |>
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |>
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot()

nyc_airbnb |>
  filter(price < 1000, 
         room_type == "Entire home/apt", 
         borough == "Manhattan") |>
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |>
  ggplot(aes(x = price, y = neighbourhood)) +
  geom_density_ridges()
```

# try to make a map

```{r}
nyc_airbnb |>
  filter(price < 1000, 
         room_type == "Entire home/apt", 
         borough == "Manhattan") |>
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()
```

# try something else entirely

```{r}
nyc_airbnb |>
  filter(price < 1000, 
         room_type == "Entire home/apt", 
         borough == "Manhattan") |>
  sample_n(500) |>
  leaflet() |>
  addProviderTiles(providers$CartoDB.Positron) |>
  addCircleMarkers(~lat, ~long, radius = .5)
```

# attempt solutions